Fivebranes

### 2022-04-04 fivebranes/fivebranes.tex
index one fivebrane
local

\newcommand\thooft{`t Hooft\,}

@@

>>>>

@@

\section{Careful index computation}

Let's compute the index of a single fivebrane.

\begin{table}[htbp]
\centering
\begin{tabular}{llrrr}
 & $t_1$ & $t_2$ & $q$ & $r$ \\
$z_1$ & $1$ & 0 & 0 & $-1$\\
$z_2$ & $-1$ & $1$ & 0 & $-1$\\
$z_3$ & $0$ & $-1$ & 0 & $-1$\\
$w_1$ & $0$ & $0$ & $1$ & $3/2$\\
$w_2$ & 0& 0 & $-1$ & $3/2$ \\
\\
\end{tabular}
\caption{Assignment of fugacities}
\end{table}

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- r^3 \frac{t_1 r^{-1} + t_1^{-1} t_2 r^{-1} + t_2^{-1} r^{-1} }{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
r^3 \frac{1}{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)} 
\]
\item Single particle operators on $K^{-1/2} \otimes \C^2$ contribute
\[
f_{single} (t_1,t_2,q,r) = r^{\frac32} \frac{q + q^{-1}}{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)}
\]
\end{itemize}

Putting this all together we get 
\[
f_{tensor} (t_1,t_2,q,r) = \frac{(q + q^{-1})r^{\frac32} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )r^2 + r^3}{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)} 
\]

The specialization $t_1=t_2$ and $q=r=1$ is
\[
f_{tensor}(t_1,t_2=t_1, q=1,r=1) = \frac1{1-t_1} .
\]

\section{random}

The non minimal twist of the tensor is $\Omega^\bu(\R^4) \otimes \Omega^{1,\bu}(\C_z)$.
Omega-background in one $\R^2$ gives $\Omega^\bu(\R^2) \otimes \Omega^{1,\bu}(\C_z)$.
Looks like a deformation of $\Omega^{0,\bu}(\C_w) \otimes \Omega^{1,\bu}(\C_z) [\ep]$ by the Kapustin twist $\ep \frac{\del}{\del w}$.
